New_Data_Coherence

### 2019-10-06 Analysis/Coherence_Calculations_New.Rmd
latest tables

#Adding p-values from permutation test
#Biogrid
biogrid_p = readRDS("./data/Permutation_Results/biogrid_p_1k.rds") %>% as.data.frame(.) %>% dplyr::select(-new_coherence)

@@

#String Filtered
string_filt_p = readRDS("./data/Permutation_Results/string_filt_p_1k.rds") %>% as.data.frame(.)  %>% dplyr::select(-new_coherence)

>>>>

#Adding p-values from permutation test
#Biogrid
biogrid_p = readRDS("./data/Permutation_Results/Complete_10k_Biogrid.rds") %>% as.data.frame(.) %>% dplyr::select(-new_coherence)

@@

#String Filtered
string_filt_p = readRDS("./data/Permutation_Results/Complete_10k_String_Filt.rds") %>% as.data.frame(.)  %>% dplyr::select(-new_coherence)
